\documentclass[a4paper,11pt,oneside]{article}

% Note thad usimg a spel chequer (e.g. ispell, aspell) is generolz
% a very guud ideo.

\usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm]{geometry}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{helvet}
\usepackage{parskip}		   %% blank lines between paragraphs, no indent
\usepackage[pdftex]{graphicx}	%% include graphics, preferrably pdf
\usepackage[pdftex]{hyperref}	%% many PDF options can be set here
\usepackage{shellesc}           %% run shell commands if you need
\usepackage{yhmath}%
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{subcaption}
\usepackage{lipsum}
\usepackage{calc}

\pdfadjustspacing=1		%% force LaTeX-like character spacing

\newcommand{\myname}{Lalit Singh}
\newcommand{\mytitle}{Web Traffic Prediction using Echo State Networks}
\newcommand{\mysupervisor}{Prof. Herbert Jaeger}

\hypersetup{
  pdfauthor = {\myname},
  pdftitle = {\mytitle},
  pdfkeywords = {},
  colorlinks = {true},
  linkcolor = {blue}
}



\begin{document}
  \pagenumbering{roman}
  \input{./coverPage/coverPage.tex}
  
  \input{./acknowledgement/acknowledgement.tex}
  

  \input{./abstract/abstract.tex}

  \newpage
  \tableofcontents

  \clearpage
  \pagenumbering{arabic}
  
  % This, like the rest, addresses fellow experts from your field (but
  % not from your particular topic of research). Here you should
  % technically connect to the main concepts from that field and give an
  % outline of your project, stating the research/engineering question
  % that you want to get answered by your project.
  \input{./introduction/introduction.tex}
  
  \section{Statement and Motivation of Research}

  This part should make clear which question, exactly, you are 
  pursuing, and why your project is relevant/interesting. This is the
  place to cite relevant literature. Where does your project extend
  the state of the art? What weaknesses in known approaches do you
  hope to overcome? If you have carried out preliminary experiments,
  describe them here.

  (target size: 3-5 pages)

 \input{./backgroundConcepts/backgroundConcepts.tex}
  

  \section{Description of the Investigation}
  
  \input{./description/description.tex}



  \section{Evaluation of the Investigation}

  This section discusses criteria that are used to evaluate the
  research results. Make sure your results can be used to published
  research results, i.e., to the already known state-of-the-art.



  \section{Conclusions}

  Summarize the main aspects and results of the research
  project. Provide an answer to the research questions stated earlier.

  (target size: 1/2 page)

  \nocite{JS06}

  \newpage
  \bibliographystyle{unsrt}
  \bibliography{bibliography}

\end{document}

